Title Text

### 2014-04-09 intromoa.tex
more edits
more edits for clarity

Note
also that all operations are over the 0th axis. The operator $\Omega$~\cite{mul88} extends operations over all other dimensions.
\subsubsection*{Example}
Consider the evaluation of the following expression using the
3 by 5 by 4 array, $A$, introduced in Section~\ref{indshp}.
\begin{eqnarray}
             <1\;\; 2> \psi (2 \take \Phi A) 
\end{eqnarray}
where A is the array given in the previous section.
The shape of the result is 
\begin{eqnarray}
                & &  2 \drop s_{(2 \take \Phi A)} \nonumber \\
                & = & 2 \drop (<2> \cat (1 \drop s_{\Phi A} )) \nonumber \\
               & = & 2 \drop (<2> \cat (1 \drop s_A)) \nonumber \\
               & = & 2 \drop (<2> \cat <5\; 4>) \nonumber \\
               & = & 2 \drop <2\; 5 \;4> \nonumber \\
              &  = &<4> . 
\end{eqnarray}
The expression can be simplified using the definitions:
\begin{eqnarray}
          &&   <1\; 2> \psi (2 \take \Phi A) \nonumber \\
           & = &  <1 \; 2> \psi \Phi A \nonumber \\
         &   = & <2> \psi (<1> \psi \Phi A) \nonumber \\
         &  = & <2> \psi (<3 - 1 - 1 > \psi A) \nonumber \\
        &   = & <1 \; 2> \psi A  \nonumber \\
\end{eqnarray}
This process of simplifying the expression for the item in terms of
its Cartesian coordinates is called {\em Psi Reduction}. The operations of MoA
have been designed so that all expressions can be reduced to a minimal
normal form~\cite{mul88}.
Some MoA operations defined by {\em psi} are found in Fig.\ref{moa}.

>>>>

Note
also that all operations are over the 0th axis. The operator $\Omega$~\cite{mul88} extends operations over all other dimensions.
\subsubsection*{Example}
Consider the evaluation of the following expression using the
3 by 5 by 4 array, $A$, introduced in Section~\ref{indshp}.
\begin{eqnarray}
             <1\;\; 2> \psi (2 \take \Phi A) 
\end{eqnarray}
where A is the array given in the previous section.
The shape of the result is 
\begin{eqnarray}
                & &  2 \drop s_{(2 \take \Phi A)} \nonumber \\
                & = & 2 \drop (<2> \cat (1 \drop s_{\Phi A} )) \nonumber \\
               & = & 2 \drop (<2> \cat (1 \drop s_A)) \nonumber \\
               & = & 2 \drop (<2> \cat <5\; 4>) \nonumber \\
               & = & 2 \drop <2\; 5 \;4> \nonumber \\
              &  = &<4> . 
\end{eqnarray}
The expression can be simplified using the definitions:
\begin{eqnarray}
          &&   <1\; 2> \psi (2 \take \Phi A) \nonumber \\
           & = &  <1 \; 2> \psi \Phi A \nonumber \\
         &   = & <2> \psi (<1> \psi \Phi A) \nonumber \\
         &  = & <2> \psi (<3 - 1 - 1 > \psi A) \nonumber \\
        &   = & <1 \; 2> \psi A  \nonumber \\
&=&\mbox {Thus,} \;\;\forall \;\; j \;\;\ni \;\;0 \leq j < 4 \nonumber \\
&=& = <j>  \psi <1 \; 2> \psi A  \nonumber \\
&=& <1\:2\;j\;> \psi A \nonumber\\
\end{eqnarray}

This process of simplifying expression (1) in terms of
its Cartesian coordinates is called {\em Psi Reduction}. The operations of MoA
have been designed so that all expressions can be reduced to a minimal
normal form~\cite{mul88}, the DNF.
Some MoA operations defined by {\em psi} are found in Fig.\ref{moa}.
